Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
fix citation
minor fixes

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
$9\%$\comments{($23$ misses)} of the $\numFaults{}$ cases and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves 
the diagnostic accuracy up to $73.7\%$ (\avgImprov\ on average)\Sof{Calculei
mal a média antes. A melhoria média para o top-5 é 9.6\% e a máxima
melhoria que a técnica atingiu foi de 96.7\%. Eu reportei aqui no abstract para o
top-10 porque a \% de melhoria é maior. Se vocês acharem que é mais vantajoso
reportar os valores do top-10, avisem. Podemos reportar ambas. Atenção, só considero
os casos em que pelo menos uma das variantes obteve melhoria}. To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

Model-based diagnosis is a well-known approach that has been proposed by the
DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.
\Sof{A primeira citação estava repetida. @Rui, por favor, verifica se a segunda é a que eu introduzi
mayer2008prioritising ou se é outra ou então se estava repetida por engano.}

@@

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\Fix{cite}\Sof{Not sure what to cite here}. A fault of omission occurs when
the program is buggy because some code is missing, i.e., a bug that is 
corrected by adding code. Intuitivelly, the ability of techniques to
produce good diagnosis in those cases is poor since fault of omission
are non-executable statements which means that the execution information
cannot help locate the fault directly. A total of $59.7\%$ of the cases 
in this dataset manifest fault of omission, which is a good indication of 
difficulty\Sof{note to self: Improve the good indication of difficulty}.

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/boxplot_>0.pdf}
		\caption{Boxplot of $\Delta{}C$. \Sof{Considering only the best cases}}
		\label{fig:boxplot}
\end{figure}

\begin{figure}[h]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/boxplot_all.pdf}
		\caption{Boxplot of $\Delta{}C$. \Sof{Considering the best cases and the \textbf{top-misses}}}
		\label{fig:boxplot}
\end{figure}

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
$9\%$\comments{($23$ misses)} of the $\numFaults{}$ cases and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves
the diagnostic accuracy up to $73.7\%$ (\avgImprov\ on average). To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

Model-based diagnosis is a well-known approach that has been proposed by the
DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.

@@

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\cite{Pearson:2017:EIF:3097368.3097441,just-defects4j-issta2014}. 
A fault of omission occurs when
the program is buggy because some code is missing, i.e., a bug that is
corrected by adding code. Intuitivelly, the ability of techniques to
produce accurate diagnostic reports in those cases is poor since fault of omission
are non-executable statements which means that the execution information
cannot help locate the fault directly. A total of $59.7\%$ of the cases
in this dataset manifest fault of omission, which is a good indication of
difficulty\Sof{note to self: Improve the good indication of difficulty}.

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.47\textwidth]{figures/double-boxplot.pdf}
		\caption{Boxplot of $\Delta{}C$.}
		\label{fig:boxplot}
\end{figure}
%
% \begin{figure}[h]
% 		\centering
% 		\includegraphics[width=0.42\textwidth]{figures/boxplot_all.pdf}
% 		\caption{Boxplot of $\Delta{}C$. \Sof{Considering the best cases and the \textbf{top-misses}}}
% 		\label{fig:boxplot}
% \end{figure}
